This PDF is a Git Repository\\Containing its Own \LaTeX\ Source\\and a Copy of Itself

### 2017-05-02 article.tex
More text

So, where can we put a 5-byte DEFLATE header such that it won't
corrupt the PDF? We could use our standard trick of putting it in a
PDF object stream that we've exploited countless times before to
enable PoC$\|$GTFO polyglots. The trouble with that is that object
streams are fixed-length, so once the PDF is decompressed
(\textit{i.e.},~when a repo is cloned from the git bundle), then all
of the 5-byte DEFLATE headers will disappear and the object stream
lengths would all be incorrect. Instead, I chose to use PDF comments,
which start at any occurrence of the percent sign character~(\%)
outside a string or stream and continue until the first occurrence of
a newline.  All of the PDF viewers I tested don't seem to care if
comments include non-ASCII characters; they seem to simply scan for a
newline. Therefore, we can inject ``\texttt{\%\textbackslash n}''
between PDF objects and move the DEFLATE headers there. The only
caveat is that the DEFLATE header itself can't contain a newline
byte~(\texttt{0x0A}), otherwise the comment would be ended
prematurely.  We can resolve that by adding extra spaces to the end of
the comment, increasing the length of the following DEFLATE block and
thus increasing the length bytes in the DEFLATE header and avoiding
the \texttt{0x0A}. The only concession made with this approach is that
PDF Xref offsets in the deflated version of the PDF will be off by a
multiple of 5, due to the removed DEFLATE headers. Fortunately, most
PDF readers can gracefully handle incorrect Xref offsets (at the
expense of a slower loading time), and this will only affect the PDF
contained in the repository, \emph{not} the PDF polyglot.

>>>>

Where can we put a 5-byte DEFLATE header such that it won't corrupt
the PDF? We could use our standard trick of putting it in a PDF object
stream that we've exploited countless times before to enable
PoC$\|$GTFO polyglots. The trouble with that is that object streams
are fixed-length, so once the PDF is decompressed (\textit{i.e.},~when
a repo is cloned from the git bundle), then all of the 5-byte DEFLATE
headers will disappear and the object stream lengths would all be
incorrect. Instead, I chose to use PDF comments, which start at any
occurrence of the percent sign character~(\%) outside a string or
stream and continue until the first occurrence of a newline.  All of
the PDF viewers I tested don't seem to care if comments include
non-ASCII characters; they seem to simply scan for a
newline. Therefore, we can inject ``\texttt{\%\textbackslash n}''
between PDF objects and move the DEFLATE headers there. The only
caveat is that the DEFLATE header itself can't contain a newline
byte~(\texttt{0x0A}), otherwise the comment would be ended
prematurely.  We can resolve that by adding extra spaces to the end of
the comment, increasing the length of the following DEFLATE block and
thus increasing the length bytes in the DEFLATE header and avoiding
the \texttt{0x0A}. The only concession made with this approach is that
PDF Xref offsets in the deflated version of the PDF will be off by a
multiple of 5, due to the removed DEFLATE headers. Fortunately, most
PDF readers can gracefully handle incorrect Xref offsets (at the
expense of a slower loading time), and this will only affect the PDF
contained in the repository, \emph{not} the PDF polyglot.

As a final step, we need to update the SHA-1 sum at the end of the
packfile~(\textit{q.v.}~Section~\ref{sec:GitBundleFormat}), since we
moved the locations of the DEFLATE headers, thus affecting the hash.

At this point, we have all the tools necessary to create a generalized
PDF/Git Bundle polyglot for \emph{almost} any PDF and git
repository. The only remaining hurdle is that some viewers require
that the PDF occur as early in the packfile as possible. At first, I
considered applying another patch directly the git source code to make
the uncompressed object first in the packfile. This approach proved to
be very involved, in part due to git's UNIX design philosophy and
architecture of generic code reuse. We're already updating the
packfile's SHA-1 hash due to changing the DEFLATE headers, so instead
I decided to simply reorder the objects after-the-fact, subsequent to
the DEFLATE header fix but before we update the hash. The only
challenge is that moving objects in the packfile has the potential to
break offset delta objects, since they refer to their base objects via
a byte offset within the packfile.  Moving the PDF to the beginning
will break any offset delta objects that occur after the original
position of the PDF which refer to base objects that occur before the
original position of the PDF. That's why I had to dive deeper into the
rabbit hole of the packfile format to understand the delta object
headers (as you saw at the end of Section~\ref{sec:GitBundleFormat},
if you were brave enough to finish it), since I originally attempted
to rewrite the broken ones. Rewriting the broken offset delta objects
is the \emph{correct} solution, but, in the end, I discovered a much
simpler way.

\begin{center}
\begin{tikzpicture}
\node at (0,0) (text) {\begin{minipage}{0.8\hsize}\small
As a matter of fact, G-d just questioned my judgement. He said,
`Terry, are you worthy to be the man who makes the temple? If you are,
you must answer: Is this [dastardly], or is this divine intellect?'
\end{minipage}};
\node[anchor=north east] at (text.north west) {\LARGE``};
\node[anchor=south west] at (text.south east) {\LARGE''};
\node[anchor=north east] at (text.south east) (terry) {\setbox9=\hbox{\llap{---}Terry A.\ Davis, creator of TempleOS}\parbox{\wd9}{\raggedright\box9 self-proclaimed ``smartest programmer that's ever lived''}};
\end{tikzpicture}
\end{center}

In the previous section, recall that we created the minimal PoC by
patching the command line arguments to \texttt{pack-objects}.  One of
the command line arguments that is already passed by default
is \texttt{--delta-base-offset}. Running \texttt{git help
pack-objects} reveals the following:
\begin{center}
{\footnotesize\setbox9\hbox{\verb|A packed archive can express the base object of a delta as either a|}
\begin{minipage}{\wd9}
\begin{verbatim}
A packed archive can express the base object of a delta as either a
20-byte object name or as an offset in the stream, but ancient
versions of Git don't understand the latter. By default, git
pack-objects only uses the former format for better compatibility.
This option allows the command to use the latter format for
compactness. Depending on the average delta chain length, this
option typically shrinks the resulting packfile by 3-5 per-cent.
\end{verbatim}
\end{minipage}}
\end{center}
So all we need to do is \emph{remove} the \texttt{--delta-base-offset}
argument and git will not include any offset delta objects in the
pack!
